\texttt{thornado}-transport: IMEX schemes for two-moment neutrino transport respecting Fermi-Dirac statistics

### 2018-09-28 Documents/M1/Astronum_2018/sections/intro.tex
Modified the introduction section.

To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a constraint-preserving diffusion accurate IMEX schemes for ensure a valid result.
Here is the explanation.
First of all, the Boltzmann transport equation is a nonlinear equation.
Its integral form which gives the two-moment method requires the information of $(i+1)$-th order moment for $i$-th order moment evolution.
Therefore, two-moment method needs a algebraic closure which gives a approximated value of the second order moment $\bcK$ given $\cJ$ and $\bcH$.
Second, the angular moments are confined. Since a neutrino distribution function is confined ($f\in(0,1)$) by the Pauli exclusion principle, its moments as integrals of a confined function over confined domain ($\omega\in\bbS^{2}$) are also confined.
We call the moments satisfying a Fermi-Dirac statistics realizable moments.
Hence, the algebraic closure should give a realizable $\bcK$ and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a constraint-preserving IMEX.
Fourth, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.\ee{why?}. 
Moment realizabilty and diffusion accurate IMEX scheme motivates this work

This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and realizability algebraic closures in the context of Fermi-Dirac statistics;
Section~\ref{se:SpacialDiscretization} we discuss moment realizability in the context of a first-order finite volume spatial discretization; Section~\ref{se:TimeIntegration} discusses how to construct a constraint-preserving, diffusion limit accurate IMEX (PD-ARS) scheme and two PD-ARS schemes are presented %\ee{should we introduce the term PD-ARS here?};
Section~\ref{se:NumericalTests} gives the result of the numerical tests of the PD-ARSs; Section~\ref{se:Conclusion} is the conclusion section.

>>>>

To employing IMEX schemes for two-moment neutrino transport, two things need to be chosen carefully: a Fermi-Dirac statistics satisfied algebraic closure for closing the two-moment equations and a constraint-preserving diffusion accurate IMEX schemes for ensure a valid result.
Here is the explanation.
First of all, the Boltzmann transport equation is a nonlinear equation.
Its integral form which gives the two-moment method requires the information of $(i+1)$-th order moment for $i$-th order moment evolution.
Therefore, two-moment method needs a algebraic closure which gives a approximated value of the second order moment $\bcK$ given $\cJ$ and $\bcH$.
Second, the angular moments are confined. Since a neutrino distribution function is confined ($f\in(0,1)$) by the Pauli exclusion principle, its moments as integrals of a confined function over confined domain ($\omega\in\bbS^{2}$) are also confined.
We call the moments satisfying a Fermi-Dirac statistics realizable moments.
Hence, the algebraic closure should give a realizable $\bcK$ and the well-posedness of closure requires realizable $\cJ$ and $\bcH$.
Third, the realizability of $\cJ$ and $\bcH$ on each time step requires a constraint-preserving IMEX.
Since the realizable moments form a convex set, it is possible to construct a constraint-preserving IMEX for two-moment neutrino transport method.
Fourth, the physics of neutrino transport in CCSNe requires the IMEX be diffusion limit accurate.
[citation] showed standard IMEX scheme can't have an order higher than first.
To have second-order (or higher-order) accuracy, some correction steps are needed.
However, the correction step can deteriorate the accuracy of the IMEX in the diffusion limit and restrict the time step.
To keep simple, we focus on the IMEX scheme without correction step and require it high-order (second or higher order) in the streaming limit and diffusion accurate.
We call these IMEX scheme PD-ARS.
The study of moment realizabilty and constraint-preserving diffusion accurate IMEX scheme motivates this work.

This paper is recognized as following: Section~\ref{se:Two-MomentModel} discusses the mathematical model, algebraic closures, and the constraints on the moments and algebraic closures imposed by Fermi-Dirac statistics;
Section~\ref{se:SpacialDiscretization} gives a first-order finite volume spatial discretization and shows how the spatial discretization preserve constraints in a IMEX step;
Section~\ref{se:TimeIntegration} discusses how to use convex combination to construct PD-ARS and two PD-ARSs, one has second-order in the streaming limit and the other has third-order, are provided;
Section~\ref{se:NumericalTests} presents the results of the numerical tests which demonstrate the portieres of the PD-ARSs; Section~\ref{se:Conclusion} summaries the achievement of this paper.
